

\begin{thebibliography}{5}
	
\bibitem{tuto1989} L. R. Rabiner, "A tutorial on hidden Markov models and selected applications in speech recognition", \emph{Proceedings of the IEEE}, vol. 77, pp. 257-286, 1989, ISSN 0018-9456.
\bibitem{cont2013} Ghazaleh Panahandeh, Nasser Mohammadiha, Arne Leijon, Peter Handel, "Continuous Hidden Markov Model for Pedestrian Activity Classification and Gait Analysis", \emph{Instrumentation and Measurement IEEE Transactions on}, vol. 62, pp. 1073-1083, 2013, ISSN 0890-6955, DOI 10.1109/5.18626
\bibitem{towa2009} Guangyi Shi and Yuexian Zou and Yufeng Jin and Xiaole Cui and W. J. Li, "Towards HMM based human motion recognition using MEMS inertial sensors", \emph{2008 IEEE International Conference on Robotics and Biomimetics}, pp. 1762-1766, 2009, DOI 10.1109/ROBIO.2009.4913268.
\bibitem{ches2012} G. Panahandeh and N. Mohammadiha and A. Leijon and P. Handel, "Chest-mounted inertial measurement unit for pedestrian motion classification using continuous hidden Markov model", \emph{2012 IEEE International Instrumentation and Measurement Technology Conference Proceedings}, pp. 991-995, 2012, ISSN 1091-5281, DOI 10.1109/I2MTC.2012.6229380.
\bibitem{thre_2001} I. P. I. Pappas, M. R. Popovic, T. Keller, V. Dietz, and M. Morari, “A
reliable gait phase detection system,” \emph{IEEE Trans. Neural Syst. Rehabil.
	Eng.}, vol. 9, no. 2, pp. 113–125, Jun. 2001.
\bibitem{fuzz_} C. Senanayake and S. Senanayake, “Computational intelligent gait-phase
detection system to identify pathological gait,” \emph{IEEE Trans. Inf. Technol.
	Biomed.}, vol. 14, no. 5, pp. 1173–1179, Sep. 2010.
\bibitem{biol1998} R. Durbin and S. Eddy and A. Krogh and G. Mitchison, Markov chains and hidden Markov models", in \emph{Biological sequence analysis}, UK: Cambridge University Press, 1998, pp. 46-79.
\bibitem{thes2011}G. Pfundstein, "Hidden Markov Models with Generalised Emission Distribution for Analysis of High-Dimensional, Non-Euclidean Data," M.S. thesis, Dept. Stat. and Gene Center, Munich Univ., Munich, Germany, 2011.
\bibitem{tool2001} Huseyin M. Ertunc and Kenneth A. Loparo and Hasan Ocak, "Tool wear condition monitoring in drilling operations using hidden Markov models (HMMs)", \emph{International Journal of Machine Tools and Manufacture}, vol. 41, no. 9, pp. 1363-1384, 2001, ISSN 0018-9456, DOI https://doi.org/10.1016/S0890-6955(00)00112-7. [Online]. Available:  http://www.sciencedirect.com/science/article/pii/S0890695500001127
\bibitem{effi2016} Mingxia Liu and Daoqiang Zhang, "Feature selection with effective distance", \emph{Neurocomputing}, vol. 215, no. Supplement C, pp. 100-109, 2016, note SI: Stereo Data, ISSN 0925-2312, DOI https://doi.org/10.1016/j.neucom.2015.07.155. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0925231216306336. 
\bibitem{twop2008} Ali Mahvash and Annie Ross, "Two-phase flow pattern identification using continuous hidden Markov model", \emph{International Journal of Multiphase Flow}, vol. 34, no. 3, pp. 303-311, 2008, ISSN 0301-9322, DOI https://doi.org/10.1016/j.ijmultiphaseflow.2007.08.006. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0301932207001462. 
\bibitem{newh2016} Saul Solorio-Fernandez and J. Ariel Carrasco-Ochoa and José Fco. Martínez-Trinidad, "A new hybrid filter–wrapper feature selection method for clustering based on ranking", \emph{Neurocomputing}, vol. 214, no. Supplement C, pp. 866-880, 2016, ISSN 0925-2312, DOI https://doi.org/10.1016/j.neucom.2016.07.026. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0925231216307718. 
\bibitem{hybr2011} Hui-Huang Hsu and Cheng-Wei Hsieh and Ming-Da Lu, "Hybrid feature selection by combining filters and wrappers", \emph{Expert Systems with Applications}, vol. 38, no. 7, pp. 8144-8150, 2011, ISSN 0957-4174, DOI https://doi.org/10.1016/j.eswa.2010.12.156. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0957417410015198. 
\bibitem{sima2013} Jeong-Su Han and Sang Wan Lee and Zeungnam Bien, "Feature subset selection using separability index matrix", \emph{Information Sciences}, vol. 223, no. Supplement C, pp. 102-118, 2013, ISSN 0020-0255, DOI https://doi.org/10.1016/j.ins.2012.09.042. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0020025512006354. 
\bibitem{maha2013} Zhao Yongli and Zhang Yungui and Tong Weiming and Chen Hongzhi, "An improved feature selection algorithm based on MAHALANOBIS distance for Network Intrusion Detection", \emph{PROCEEDINGS OF 2013 International Conference on Sensor Network Security Technology and Privacy Communication System}, pp. 69-73, 2013, DOI 10.1109/SNS-PCS.2013.6553837.
\bibitem{prtool} Dimension Reduction - Pattern Recognition Tools.[Online]. Available: http://37steps.com/prtools/examples/dimension-reduction/
\bibitem{lda2015} Youness Aliyari Ghassabeh and Frank Rudzicz and Hamid Abrishami Moghaddam, "Fast incremental LDA feature extraction", \emph{Pattern Recognition}, vol. 48, no. 6, pp. 1999-2012, 2015, ISSN 0031-3203, DOI https://doi.org/10.1016/j.patcog.2014.12.012. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S0031320314005214.
\bibitem{dime2017} Miguel Simão and Pedro Neto and Olivier Gibaru, "Using data dimensionality reduction for recognition of incomplete dynamic gestures", \emph{Pattern Recognition Letters}, vol. 99, no. Supplement C, pp. 32-38, 2017, ISSN 0167-8655, DOI https://doi.org/10.1016/j.patrec.2017.01.003. [Online]. Available: http://www.sciencedirect.com/science/article/pii/S016786551730003X.
\bibitem{pendu2004} Timothy M. Griffin and Russell P. Main and Claire T. Farley, "Biomechanics of quadrupedal walking: how do four-legged animals achieve
inverted pendulum-like movements?", \emph{The Journal of Experimental Biology}, vol. 207, pp. 3545-3558, 2004, DOI 10.1242/jeb.01177.
\bibitem{mat-feat} Feature Selection - MathWorks.[Online]. Available: https://www.mathworks.com/help/stats/feature-selection.html
\bibitem{knnc} K-Nearest Neighbor Classifier - Pattern Recognition Tools.[Online]. Available: http://www.37steps.com/prhtml/prtools/knnc.html
\bibitem{hmmestimate} hmmestimate - MathWorks.[Online]. Available: https://www.mathworks.com/help/stats/hmmestimate.html
\bibitem{gmm2000} McLachlan, G., and D. Peel, Finite Mixture Models. Hoboken, NJ: \emph{John Wiley \& Sons}, Inc., 2000.
\bibitem{fitgmm} fitgmdist - MathWorks.[Online]. Available:  https://www.mathworks.com/help/stats/fitgmdist.html
\bibitem{AIC_ref} Ljung, L. System Identification: Theory for the User, Upper Saddle River, NJ, Prentice-Hall PTR, 1999
\bibitem{AIC} Akaike's Information Criterion for estimated model - MATLAB aic.[Online]. Available:  https://www.mathworks.com/help/ident/ref/aic.html
\bibitem{BIC} Bayes Information Criterion - MATLAB - MathWorks.[Online]. Available: https://www.mathworks.com/help/stats/gmdistribution.bic.html
\bibitem{matlab-hmm} Qiuqiang Kong, "matlab-hmm".[Online]. Available: https://github.com/qiuqiangkong/matlab-hmm
\bibitem{featsel} Trainable mapping for forward feature selection - Pattern Recognition Tools. [Online] . http://www.37steps.com/prhtml/prtools/featself.html
\bibitem{maha} Mahalanobis distance - Pattern Recognition Tools. [Online] http://www.37steps.com/prhtml/prtools/distmaha.html
\bibitem{pcam} Principal component analysis (PCA or MCA on overall covariance matrix) - Pattern Recognition Tools. [Online] http://www.37steps.com/prhtml/prtools/pcam.html
\bibitem{ldam} Optimal discrimination linear mapping (Fisher mapping, LDA) - Pattern Recognition Tools. [Online]. http://www.37steps.com/prhtml/prtools/fisherm.html
\bibitem{cvpartition} Create cross validation partition for data - MATLAB - MathWorks.[Online]. https://www.mathworks.com/help/stats/cvpartition.html
\bibitem{gendat} Random sampling of datasets for training and testing - Pattern Recognition Tools. [Online]. http://www.37steps.com/prhtml/prtools/gendat.html
\bibitem{prtool-home} PRTools - A Matlab toolbox for pattern recognition.[Online]. http://prtools.org/
\bibitem{matlab-stats} Statistics and Machine Learning Toolbox - MATLAB - MathWorks.[Online]. https://www.mathworks.com/products/statistics.html
\end{thebibliography}